Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-02 bbbq_article.tex
Correctly cite msa, fix https://github.com/richelbilderbeek/bbbq_article/issues/68

To detect the evolutionary conservation of TMHs,
we create an alignment using msa, that uses msaClustalW in the back,
create a consensus sequence, determine the topology of the consensus
using the FLU transition matrix,
measure the topology of it, then estimate the conservation values.

>>>>

To detect the evolutionary conservation of TMHs,
we first selected all unique protein sequences per
gene from all 45k SARS-CoV-2 proteomes,
resulting in around 500 unique protein sequences per gene.
From the unique protein sequences, we made an alignment per gene,
using the msa \cite{bodenhofer2015msa} R package, 
using default settings, including the use of the default alignment tool
ClustalW \cite{thompson1994clustal}.
Per alignment, we used msa to determine the consensus sequence
and the conservation scores.
Per consensus sequences, the topology was determined using pureseqtmr.

\richel{use the FLU transition matrix?}
